Molecular dynamics simulation of synchronization in driven particles

### 2021-01-29 manuscript/manuscript_ajp_2020.tex
put Brownian motion into manuscript and updated code to make figure

  % (a) 
  In simulation we define our temperature parameter to
  $k_b T/E_0 \rightarrow T$
  since we set the constants to unity.
  In these units we can compare 
  simulation temperature directly
  to force 
  in order to estimate the degree of random fluctuation.
  For instance, 
  with
  no applied driving force,
  the minimum temperature required for a single particle
  to hop between minima in the potential landscape is
  $T_{min} > A_p$.
  Assuming a particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  Measure the position vs. time
  of a non-driven colloid for $T/A_p = 2.0, 4.0, 6.0$
  and note  a particle will hop a barrier
  for sufficiently high $T/A_p$ ratios.
  We find the crossover
  to a hopping regime at $T/A_p \approx 5.6$
  %when

>>>>

  % (a) 
  In simulation we define our temperature parameter to
  $k_b T/E_0 \rightarrow T$
  since we set the constants to unity.
  In these units we can compare 
  simulation temperature directly
  to force 
  in order to estimate the degree of random fluctuation.
  For instance, 
  with
  no applied driving force,
  the minimum temperature required for a single particle
  to hop between minima in the potential landscape is
  $T_{min} > A_p$.
  Assuming a particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  Measure the position vs. time
  of a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$
  and note  a particle will hop a barrier
  for sufficiently high $T/A_p$ ratios.
  We find the crossover
  to a hopping regime at $T/A_p \approx 5.6$
  %when
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
